Compiling refinement types to dependent types

### 2020-07-25 tex/paper.tex
Add values to the syntax
Add \evalsto command and terminal
Surface language operational semantics
Also write a few words about the surface language operational semantics

\newcommand{\unit}{\textbf{u}}
\newcommand{\Unit}{\textbf{Unit}}
\newcommand{\unitc}{\hat{\textbf{u}}}
\newcommand{\Unitc}{\widehat{\textbf{Unit}}}
\newcommand{\Int}{\textbf{Int}}
\newcommand{\ctxok}{\text{~ok}}
\newcommand{\fresh}{\text{~fresh name}}

@@

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{es}{\varepsilon}
\newnonterm{ec}{\hat\varepsilon}
\newnonterm r \rho
\newnonterm{ts}{\tau}
\newnonterm{tc}{\hat\tau}
\newnonterm s s
\newnonterm l l
\newnonterm B B
\newnonterm G \Gamma
\newnonterm{GC}{\hat\Gamma}

@@

The syntax of the surface language is presented in \figref{surface_syntax}.

The typing rules for the surface language are laid out in \figref{surface_typing}.
For the type well-formedness and term typing rules
we also assume each of them has a premise $\nonterm G \ctxok$
stating that the context is well-formed.

\begin{figure}[ht]
  \footnotesize
  \begin{subfigure}{.6\textwidth}
    \nonterms{es,l}
    \caption{Term level}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \nonterms{G,r,B,ts}
    \caption{Type level}
  \end{subfigure}
  \caption{Surface language syntax}
  \label{fig:surface_syntax}
\end{figure}

@@

>>>>

\newcommand{\unit}{\textbf{u}}
\newcommand{\Unit}{\textbf{Unit}}
\newcommand{\unitc}{\hat{\textbf{u}}}
\newcommand{\Unitc}{\widehat{\textbf{Unit}}}
\newcommand{\Int}{\textbf{Int}}
\newcommand{\ctxok}{\text{~ok}}
\newcommand{\fresh}{\text{~fresh name}}
\newcommand{\evalsto}{\rightsquigarrow}

@@

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{es}{\varepsilon}
\newnonterm{ec}{\hat\varepsilon}
\newnonterm r \rho
\newnonterm{ts}{\tau}
\newnonterm{tc}{\hat\tau}
\newnonterm s s
\newnonterm l l
\newnonterm B B
\newnonterm G \Gamma
\newnonterm{GC}{\hat\Gamma}
\newnonterm{vs} \varpi

@@

The syntax of the surface language is presented in \figref{surface_syntax}.
The typing rules for the surface language are laid out in \figref{surface_typing}.
For the type well-formedness and term typing rules
we also assume each of them has a premise $\nonterm G \ctxok$
stating that the context is well-formed.
The (small-step) operational semantics for the surface language are presented in \figref{surface_opsem}.
That is largely the usual call-by-value evaluation model
with some extra rules for the ADTs and pattern matching.

\begin{figure}[ht]
  \footnotesize
  \begin{subfigure}{.6\textwidth}
    \nonterms{es,l,vs}
    \caption{Term level}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \nonterms{G,r,B,ts}
    \caption{Type level}
  \end{subfigure}
  \caption{Surface language syntax}
  \label{fig:surface_syntax}
\end{figure}

@@

\begin{figure}[ht]
  \footnotesize
  \drules[E]{$\nonterm{es}_1 \evalsto \nonterm{es}_2$}{term evaluation}{AppL,AppR,AppAbs,ADT,CaseScrut,CaseMatch}
  \caption{Surface language small-step operational semantics}
  \label{fig:surface_opsem}
\end{figure}
